Supplementary material

### 2022-10-08 draft_BLC/supplementary_material.tex
shortening

>>>>

\subsubsection*{Baseline Bengali data from the SHRUTI corpus}

The SHRUTI corpus is the largest free corpus of Western Bengali speech that we are aware of. It comprises of 21.64 hours of read speech, containing 7383 unique sentences (22012 unique words) from Bengali newspapers in different domains, covering the most frequently used words of the language. The speakers are 34 adults (age range 20-40, 75\% male, 25\% female) who have grown up in the Indian state of West Bengal, and speak standard colloquial Bengali. All of the speakers have university-level education or higher. Given these parallels in linguistic, regional, and socio-economic background, we believe that Bengali speech from this corpus is representative of the average target Bengali vowel categories that are of interest in this study.
To estimate average vowel positions, we extracted formant values from syllable-initial productions of \nt{\ae} and \nt{a:}, at 55\% into the vowel, to get estimates from the steady state, which should most closely approximate the production target. Next, we compared these to our participants' productions in the non-switched English condition to understand the relative positions of these categories. This is visualized in figure \ref{vowels_unilingual_ie_bengali}.

Note that we refrained from using corpus data for average Indian English vowel positions, opting instead to use the participant data from this study, because IE has high regional variability (c.f. discussion in section \ref{bengali_english_in_india}). To the best of our knowledge, there is no freely available corpus of IE speech from Bengali speakers in India.
